\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
happy with abstract and intro

Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. If this approach proves successful it will transform how we interact with course material and learning processes in general. Ultimately, this research may be applicable to almost all areas in which knowledge is supposed to be transferred.\\

@@

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through providing context to not just provide information but rather knowledge.\\

@@

In essence, both issues stem from information being generated without enough context or structure. This makes the information hard to process by humans and/or machines. The Semantic Web hopes to change the former, whereas new, more visual presentation tools using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer. The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

@@

To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

\begin{figure}[H]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
			   \caption{Simple, explanatory slide}
                \label{fig:Annie-presentation-teacher}
        \end{subfigure}%
        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.45\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
		  \caption{Information dependencies}
                \label{fig:Annie-presentation-information}
        \end{subfigure}
        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
\end{figure}

>>>>

Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, the proposed research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. If this approach proves successful it will transform how we interact with course material and learning processes in general. Ultimately, this research may be applicable to almost all areas in which knowledge needs to be transferred.\\

@@

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through providing context, to not just provide information, but rather knowledge.\\

@@

In essence, both issues stem from information being generated without enough context or structure. This makes the information hard to process by humans and/or machines. The Semantic Web hopes to change the former, whereas new, more visual presentation tools, using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer. The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

@@

\begin{figure}[H]
        \centering
        \begin{subfigure}[b]{0.47\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
			   \caption{Simple, explanatory slide}
                \label{fig:Annie-presentation-teacher}
        \end{subfigure}%
        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.47\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
		  \caption{Information dependencies}
                \label{fig:Annie-presentation-information}
        \end{subfigure}
        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
\end{figure}

To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\
